% !TeX root = ..\dissertation.tex

\chapter*{Plan}
\begin{itemize}
	\item Title page/Title?
	\item Abstract?
	\item Acknowledgements?
	\item Table of contents?
	\item[1.] Introduction
	      \begin{itemize}
		      \item What is machine learning?
		      \item Machine learning is very complex to human understanding
		      \item Machine learning is widely used in many high stakes scenarios --- give examples
		      \item It is important to be able to look inside the `black box' of machine learning --- explain how this would be useful in each of the given examples
		      \item We can use statistical methods to try and recover the information in a ML algorithm --- give some idea how
	      \end{itemize}
	\item[2.] Literature Review
	      \begin{itemize}
		      \item Machine Learning
		      \item Neural Networks
		      \item Deep Learning
		      \item Stepwise Regression
		      \item LASSO
		      \item Gaussian Processes
		      \item Previous papers on this subject
	      \end{itemize}
	\item[3.] Results
	      \begin{itemize}
		      \item Introduce a simple example function
		      \item Possibly also use a more complex example?
		      \item Training a neural network
		            \begin{itemize}
			            \item Choosing the right size NN
			            \item Order of the input points matters
		            \end{itemize}
		      \item Fitting a linear regression
		      \item Using stepwise regression
		      \item Using LASSO
		      \item Using GPs
	      \end{itemize}
	\item[4.] Conclusion
	      \begin{itemize}
		      \item How well have each of the attempts worked?
		      \item What could be improved?
		      \item How useful would more research on this topic  be?
		      \item What should future research on this topic focus on?
	      \end{itemize}
	\item Appendices
	      \begin{itemize}
		      \item Code
		      \item Large tables of results
		      \item Large figures
	      \end{itemize}
	\item Bibliography
\end{itemize}
